Clouds and Radiation in a mock-Walker Circulation

### 2019-09-20 Silvers_WalkerCell.tex
replaced the enthalpy flux figure with a four panel figure showing the low-level variables of interest, including enthalpy.

\begin{figure}
  \centering
       %\includegraphics[width=0.96\columnwidth]{walkerfigs/hist_6pan_25vs2vs1_lwoff_lwon.eps}
       \includegraphics[width=0.96\columnwidth]{walkerfigs/hist_3pan_25vs2vs1_lwoff_lwon_draft2.eps}
  \caption{Normalized probability distributions of the location of the maximum value of precipitation for experiments with the 
  longwave CRE on.  All panels show cases with parameterized convection, the top panels are computed for the experiments 
  having a domain width of 4000 km while the bottom panels are for experiments having a domain width of 16000 km.  The 
  black curves show a Gaussian function with a standard deviation computed for each experiment and an expected location 
  in the center of the domain where the SST is warmest. }
\end{figure}

@@

% surface enthalpy flux
\begin{figure}
  \centering
  \begin{minipage}{0.4\textwidth}
    \centering
      \includegraphics[width=0.96\columnwidth]{walkerfigs/sfcenthalpyflx_3mods_lwcreOn.eps} 
    \end{minipage}
    \begin{minipage}{0.4\textwidth}
    \centering
      \includegraphics[width=0.96\columnwidth]{walkerfigs/sfcenthalpyflx_3mods_lwcreOff.eps}
    \end{minipage}
    \caption{Surface enthalpy flux (solid lines) for the three grid-spacings.  Dashed lines show the individual components 
    (latent and sensible heat flux) of the enthalpy.
    On the left are experiments with LWCRE on and on the right, the same experiments but with LWCRE off.}
    \label{fig:enthalpy}
\end{figure}

@@

When the LW CRE is off, the simulations with resolutions of 1km, 2km, and 25km all show a similar distribution and magnitude of surface 
enthalpy flux (Figure \ref{fig:enthalpy}).  However, when the LW CRE is on, there are differences between the resolutions that can be as 
large as $80 \, \rm{W/m^2}$.   These differences in surface enthalpy flux are due largely to the latent heat flux and are confined to the 
regions with ascending circulations over the warmer SST.  This manifestation of the strong interactions between clouds and the circulation 
would be entirely absent from high resolution simulations with gray radiation or fixed radiative cooling profiles.

>>>>

\begin{figure}
  \centering
       %\includegraphics[width=0.96\columnwidth]{walkerfigs/hist_6pan_25vs2vs1_lwoff_lwon.eps}
       \includegraphics[width=0.96\columnwidth]{walkerfigs/hist_3pan_25vs2vs1_lwoff_lwon_draft.eps}
  \caption{Normalized probability distributions of the location of the maximum value of precipitation for experiments with the 
  longwave CRE on.  All panels show cases with parameterized convection, the top panels are computed for the experiments 
  having a domain width of 4000 km while the bottom panels are for experiments having a domain width of 16000 km.  The 
  black curves show a Gaussian function with a standard deviation computed for each experiment and an expected location 
  in the center of the domain where the SST is warmest. }
\end{figure}

@@

\begin{figure}
  \centering
      \includegraphics[width=0.96\columnwidth]{walkerfigs/LowLevelVars_E25E2E1.eps}
  \caption{Variables important to boundary layer energy fluxes.  Top left panel shows the surface enthalpy flux ($\rm{W m^{-2}}$) and top right panel shows the equivalent potential temperature on the model level closest to the surface.  The panel on bottom left shows the $u$ wind ($\rm{m s^{-1)}}$)
  on the model level closest to the surface and the panel on bottom right shows the domain mean
  $\rm{u}$ wind.}
  \label{fig:LowLevelVars}
\end{figure}

%% surface enthalpy flux
%\begin{figure}
%  \centering
%  \begin{minipage}{0.4\textwidth}
%    \centering
%      \includegraphics[width=0.96\columnwidth]{walkerfigs/sfcenthalpyflx_3mods_lwcreOn.eps} 
%    \end{minipage}
%    \begin{minipage}{0.4\textwidth}
%    \centering
%      \includegraphics[width=0.96\columnwidth]{walkerfigs/sfcenthalpyflx_3mods_lwcreOff.eps}
%    \end{minipage}
%    \caption{Surface enthalpy flux (solid lines) for the three grid-spacings.  Dashed lines show the individual components 
%    (latent and sensible heat flux) of the enthalpy.
%    On the left are experiments with LWCRE on and on the right, the same experiments but with LWCRE off.}
%    \label{fig:enthalpy}
%\end{figure}

@@

When the LW CRE is off, the simulations with resolutions of 1km, 2km, and 25km all show a similar distribution and magnitude of surface 
enthalpy flux (Figure \ref{fig:LowLevelVars}).  However, when the LW CRE is on, there are differences between the resolutions that can be as 
large as $80 \, \rm{W/m^2}$.   These differences in surface enthalpy flux are due largely to the latent heat flux and are confined to the 
regions with ascending circulations over the warmer SST.  This manifestation of the strong interactions between clouds and the circulation 
would be entirely absent from high resolution simulations with gray radiation or fixed radiative cooling profiles.
